Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-15 paper/main.tex
switched to tr version
short version with names for distribution

\documentclass[nocopyrightspace]{sigplanconf}

@@

\titlebanner{\iffull{Extended Version}{}}%{Draft -- Do not distribute}        % These are ignored unless
\preprintfooter{\iffull{Extended Version\hspace{-.8cm}}{}}%{Draft}   % 'preprint' option specified.

@@

\authorinfo
{\iffull{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}{\vspace{-1cm}}}
{\iffull{Yale University}{\vspace{-1cm}}}

>>>>

\documentclass[nocopyrightspace,preprint]{sigplanconf}

@@

\titlebanner{\iffull{Extended Version}{}}%{Draft -- Do not distribute}        % These are ignored unless
\preprintfooter{\iffull{Extended Version\hspace{-.8cm}}{Draft\hspace{.5cm}}}%{Draft}   % 'preprint' option specified.

@@

\authorinfo
{Quentin Carbonneaux \and Jan Hoffmann \and Zhong Shao}
{Yale University \vspace{-1cm}}
